---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

Wilson et. al. suggests that you should record all the steps used when processing your raw data. This is important because it allows you to always have a way to reference back to the methods used to get your final figure or completed data analysis. If a researcher fails to do this, it can be hard to go back and figure out how you performed your analysis. This can be an issue when trying to publish your data or even when you are trying to collaborate with other people. Keeping track of your process helps you to stay organized and makes it easy to keep track of and follow your progress. R is a good tool because it allows you to have a markdown file, like this one, where you can have plain text to explain how you perform the analysis. Within the file you can also add chunks of the code. So, it can allow you to code and explain what you are doing in one file. 


3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 

x1 <- "4"
(sqrt(as.numeric(x1)))^13

[1] 8192


4) Push this homework to the GitHub repository for the homework. 





